Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-11 analysis/paper/paper.Rmd
simplify file paths and remove duplicate data files

# import the data
ma_flakes <- readxl::read_excel(here::here("data/UW Fieldschool Mau A 2015 post_excavation_season_April_2016.xlsx"),
                                col_names = FALSE)

@@

# export this data frame to use with our analysis
write_csv(ma_flakes_tr,
          here::here("data/ma_flakes_tr.csv"))

@@

# import
ma_flakes_tr <- read_csv(here::here("data/ma_flakes_tr.csv"))

@@

source(here::here("code/999-functions.R"))

@@

# export as TPS file
create_tps(polys_lmk,
           here::here("data/landmarks.tps"))

@@

plot(test_result_dorsal_cortex)

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

>>>>

# import the data
ma_flakes <- readxl::read_excel(here::here("analysis/data/raw_data/UW Fieldschool Mau A 2015 post_excavation_season_April_2016.xlsx"),
                                col_names = FALSE)

@@

# export this data frame to use with our analysis
write_csv(ma_flakes_tr,
          here::here("analysis/data/derived_data/ma_flakes_tr.csv"))

@@

# import
ma_flakes_tr <- read_csv(here::here("analysis/data/derived_data/ma_flakes_tr.csv"))

@@

source(here::here("analysis/code/999-functions.R"))

@@

# export as TPS file
create_tps(polys_lmk,
           here::here("analysis/data/derived_data/landmarks.tps"))

@@

# plot(test_result_dorsal_cortex)

@@
